\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Final revision George

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
		\end{equation}

@@

	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{WicEtAl2019} has an additional optimality property.  \cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.  This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.  Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.

	Figure~\ref{fig:OthogonalVSOblique_projection} provides geometrical intuition into the MinT method.  Suppose that the orange points in panel (a) represent in-sample forecast errors.  These provide information on the most likely direction of large deviations from the coherent subspace $\mathfrak{s}$.  This direction is denoted by $\bm{R}$.  Panel (b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection. Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace. Panel (d) depicts an oblique projection along $\bm{R}$ for all the gray points. The oblique projection yields reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If a projection is onto $\mathfrak{L}$ instead of $\mathfrak{s}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bm{\mu}^* \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

@@

	We consider ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

@@

    To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts.  For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.  Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.  This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$. The training window is then rolled forward one observation at a time until the end of the sample. This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.

    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling and MinT using a shrinkage estimator for ${\bm W}$. Squared forecast errors are computed for each series and aggregated across the whole hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.  We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate. We also include bottom-up forecasts in this comparison for completeness.

@@

    As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts. The entire boxplot for OLS reconciliation is above zero.  This is not the case for WLS and MinT which for some windows generate forecasts less accurate than the base forecasts. The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.  Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest. The average MSEs across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.

@@

\begin{equation} \label{eq:BoxCox_transformation}
	w_t =
	\begin{cases}
	\log(y_t) & \text{if}~\lambda=0;\\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{otherwise}.
	\end{cases}
\end{equation}
We first set $\lambda=0$ and hence consider only a log transformation. For the second more general Box-Cox transformation we select $\lambda$ using the ``Guerrero'' method \citep{guerrero1993time} implemented in the \verb|BoxCox.lambda()| function in the \verb|forecast| package in R \citep{Rforecast}. In order to avoid extreme and volatile transformations we restrict $\lambda \in (0.5,2)$. As zero observations exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series. This overcomes the challenge of undefined transformed values for zero observations when we specifically implement the log transformation or when $\lambda$ is selected to be zero by the ``Guerrero'' method. The constant is subtracted from the final forecasts.

After transformation we fit univariate ARIMA models to each transformed series. The \verb|auto.arima()| function in the \verb|forecast| package is used to choose the best model that minimises the AICc. Using the fitted models, forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.

The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
\begin{equation} \label{eq:BoxCox_back-transformation}
	\hat{y}_{t+h|t} =
	\begin{cases}
	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0, \\
	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}  & \text{otherwise.}
	\end{cases}
\end{equation}
These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric). Hence, the reconciled forecasts that follow from these forecasts will also be biased. We refer to these as ``Biased'' forecasts in the results that follow. This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.

@@

Using the three sets of base forecasts for each transformation, we generate coherent forecasts using the bottom-up approach but also implementing OLS, WLS and MinT reconciliation projections and compare the results for when the base forecasts are biased and bias-adjusted (unbiased). Table \ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts. Note that the conclusions that follow extend almost identically to longer forecast horizons. We do not present these here to save space but they are available upon request.

@@

In contrast to the results from using Method-1 for bias adjustment before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts. In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts. This reflects the fact and sends the warning that implementing an inappropriate bias adjustment, in this case using an additive factor rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.

\begin{table}
	\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in  \eqref{eq:BoxCox_back-transformation} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
	\label{tab:Results_MSE}
	\centering
		\begin{tabular}{lcccccc}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
			\multicolumn{3}{c}{Box-Cox Transformation}\\
			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
			Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
			Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
			OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
			MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
			WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
			Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
			\bottomrule
		\end{tabular}	
\end{table}

@@

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether is may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.

>>>>

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{0.8\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2.
		\end{equation}

@@

	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{WicEtAl2019} has an additional optimality property.  \cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.  Their choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.  Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.

	Figure~\ref{fig:OthogonalVSOblique_projection} provides geometrical intuition into the MinT method.  Suppose that the orange points in panel (a) represent in-sample forecast errors.  These provide information on the most likely direction of large deviations from the coherent subspace $\mathfrak{s}$.  This direction is denoted by $\bm{R}$.  Panel (b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$, yields a reconciled forecast closer to the target, especially compared to an orthogonal projection. Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace. Panel (d) depicts an oblique projection along $\bm{R}$ for all the gray points. The oblique projection yields reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{0.8\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If a projection is onto $\mathfrak{L}$ instead of $\mathfrak{s}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bm{\mu}^* \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

@@

	We consider ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers amongst others. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

@@

    To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts.  For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.  Using these fitted models, base forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy.  This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$. The training window is then rolled forward one observation at a time until the end of the sample. This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $129~12$-steps-ahead forecasts available for forecast evaluation.

    After obtaining the base forecasts these are reconciled using three different projection methods: OLS reconciliation, MinT using a shrinkage estimator for ${\bm W}$ and WLS reconciliation using variance scaling. Squared forecast errors are computed for each series and aggregated across the entire hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.  We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate. We also include bottom-up forecasts in this comparison for completeness.

@@

    As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts. The entire boxplot for OLS reconciliation is above zero.  This is not the case for MinT and WLS which for some windows generate forecasts less accurate than the base forecasts. The boxplots also demonstrate that OLS reconciliation is more stable than MinT and WLS reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.  Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average, which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest. The average MSE values across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.

@@

\begin{equation*} \label{eq:BoxCox_transformation}
	w_t =
	\begin{cases}
	\log(y_t) & \text{if}~\lambda=0;\\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{otherwise}.
	\end{cases}
\end{equation*}
We first set $\lambda=0$ and hence consider only a log transformation. For the second more general Box-Cox transformation we select $\lambda$ using the ``Guerrero'' method \citep{guerrero1993time} implemented in the \verb|BoxCox.lambda()| function in the \verb|forecast| package in R \citep{Rforecast}. In order to avoid extreme and volatile transformations we restrict $\lambda \in (0.5,2)$. As zero observations exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series. This overcomes the challenge of undefined transformed values for zero observations when we specifically implement the log transformation or when $\lambda$ is selected to be zero by the ``Guerrero'' method. The constant is subtracted from the final forecasts.

After transformation we fit univariate ARIMA models to each transformed series. The \verb|auto.arima()| function in the \verb|forecast| package is used to choose the best model that minimises the AICc. Using the fitted models, forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy. The same rolling window described in Section \ref{sec:comparebase} is used here as well.

The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
\begin{equation} \label{eq:BoxCox_back-transformation}
	\hat{y}_{t+h|t} =
	\begin{cases}
	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0, \\
	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}  & \text{otherwise.}
	\end{cases}
\end{equation}
These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric). Hence, the reconciled forecasts that follow from these forecasts will also be biased. We refer to these as ``Biased'' base forecasts in the results that follow. This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.

@@

Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased. Table \ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts. We note that as was the case with Section \ref{sec:comparebase} the conclusions that follow extend almost identically to longer forecast horizons. We do not present these here to save space but they are available upon request.

@@

In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts. In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts. This reflects the fact and sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.

\begin{table}
	\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via \eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in \eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
	\label{tab:Results_MSE}
	\centering
		\begin{tabular}{lcccccc}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
			\multicolumn{3}{c}{Box-Cox Transformation}\\
			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
			Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
			Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
			OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
			MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
			WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
			Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
			\bottomrule
		\end{tabular}	
\end{table}

@@

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.
